\documentclass[letter,10pt]{article} % Default font size and paper size

\usepackage{CV}

\begin{document}

\par{\centering{\Huge Thiago \textsc{Mosqueiro}}\bigskip, PhD\par}

\vspace{-0.5cm}
{\centering{\large Curriculum Vit\ae}\bigskip\par}

\vspace{-0.5cm}
\section{Contact information}

\textsc{Affiliation:} Life Sciences, University of California Los Angeles

\begin{minipage}{0.4\textwidth}
  \textsc{E-mail:} \href{mailto:thmosqueiro@ucla.edu}{thmosqueiro@ucla.edu} \\
  \textit{www:} \href{http://thmosqueiro.vandroiy.com}{thmosqueiro.vandroiy.com}
\end{minipage}
\begin{minipage}{0.5\textwidth}
  \textsc{Address:} 610 Charles E. Young Drive East. Los Angeles, Ca 90095, USA \\
\end{minipage}


\vspace{0.5cm}
\section{Work experience}

\begin{tabular}{p{3.2cm}|p{13cm}}
  \textsc{2017 March -- } & Postdoctoral researcher at \textsc{Dptmt Ecology and Evolutionary Biology}, UCLA, USA \emph{}\\
  & \footnotesize{Supervisors: Dr. Noa Pinter-Wollman}
\end{tabular}

\begin{tabular}{p{3.2cm}|p{11cm}}
  \textsc{2017 March -- } & Postdoctoral fellow at the \textsc{Collaboratory, Institute for Quantitative and Computational Biology}, UCLA, USA \emph{}\\
  & \footnotesize{Supervisors: Dr. Matteo Pellegrini}
\end{tabular}

\begin{tabular}{p{3.2cm}|p{11cm}}
  \textsc{2015 Oct -- 2017 Feb} & Postdoctoral researcher at \textsc{BioCircuits Institute}, UCSD, USA \emph{}\\
  & \footnotesize{Supervisors: Dr. Ramon Huerta \& Dr. Noa Pinter-Wollman}
\end{tabular}

\begin{tabular}{p{3.2cm}|p{11cm}}
  \textsc{2016 Sept -- Dec} & Lecturer at \textsc{Rady School of Management}, UCSD, USA \emph{}\\
  & \footnotesize{Course: Collecting and Analyzing Financial Data}
\end{tabular}

\begin{tabular}{p{3.2cm}|p{11cm}}
  \textsc{2015 Jan - March} & Junior specialist at \textsc{Rady School of Management}, UCSD, USA \emph{}\\
  & \footnotesize{Supervisor: Dr. Ramon Huerta}
\end{tabular}

\begin{tabular}{p{3.2cm}|p{11cm}}
  \textsc{2010 -- 2013} & Teaching assistant at \textsc{Institute of Physics of S\~ao Carlos}, USP, Brazil\\
  & \footnotesize{Worked with Prof. Francisco Alcaraz, Prof. Leonardo Maia, Prof. Rodrigo Pereira, Prof. Jos\'e Abel Hoyos \& Prof. Luis Nunes}\\
  & \footnotesize{Disciplines: Statistical Physics, Physics 102 and Computational Physics.}
\end{tabular}


\section{Education}

\begin{tabular}{p{3.2cm}|p{11cm}}
  \textsc{August}, 2015 & {\bf PhD in \textsc{Physics}}, \textit{University of S\~ao Paulo}, S\~ao Carlos, Brazil\\
    & Thesis: ``Information processing in sensory neural networks'' \\
    & \small Advisor: Dr. Leonardo P \textsc{Maia} \\
\end{tabular}

\begin{tabular}{p{3.2cm}|p{11cm}}
  \textsc{March} 2015 & {\bf Research internship }, \textit{University of California San Diego}, La Jolla, USA \\
  & \small Advisor: Dr. Ramon \textsc{Huerta} \\
\end{tabular}

\begin{tabular}{p{3.2cm}|p{12cm}}
  \textsc{February} 2011 & {\bf Masters in \textsc{Physics}}, \textit{University of S\~ao Paulo}, S\~ao Carlos, Brazil\\
  & Thesis: ``Optical transitions in Zincblende semiconductors heterostructures'' \\
  & \small Advisor: Dr. Esmerindo \textsc{Bernardes} \\
\end{tabular}

\begin{tabular}{p{3.2cm}|p{11cm}}
  \textsc{December} 2008 & {\bf Bachelor of Physics},
  \textit{University of S\~ao Paulo}, S\~ao Carlos, Brazil \\
\end{tabular}


\section{Grants and awards}

\renewcommand*{\arraystretch}{1.2}

\begin{longtable}{p{2.5cm}p{15cm}}
  2017 -- 2018  & Collaboratory fellowship, QCB -- UCLA \\
  2015 -- 2017  & Microsoft Azure Research grant (MS-AZR-0036P) \\
  2015 -- present  & CNPq PDE fellowship \\
  2014 -- 2015   & CAPES PSDE fellowship \\
  2014   & Selected IOP paper for novelty \& impact \\
  2013   & Yvone Mascarenhas award for best Teaching assistant \\
  2012 -- 2013 & USP PAE fellowship (teaching assistant) \\
  2009   & Best article award (The LateX Community)
\end{longtable}


\section{Peer-reviewed publications}

%For a complete list with links to slides and posters: \href{http://thmosqueiro.vandroiy.com}{thmosqueiro.vandroiy.com}
\nocite{*}

{\bf Papers in refereed journals}
\printbibliography[type=article]

{\bf Conference papers \& Talks (peer reviewed)}
\printbibliography[type=inproceedings]


\section{Invited talks}

\begin{longtable}{p{1cm}p{3.3cm}p{12cm}}
  2016  & UAM, Madrid (Spain) & Stable discrimination in accentuated divergent-convergent neural networks using data from electronic noses
 \\
 2016  & Elche (Spain) & Insect olfaction and multimodal processing of information
 \\
  2016  & HALO, Austin (USA) & Fast and stable discrimination in divergent-convergent neural networks: from Deep Learning back to Neuroscience
  \\
  2016  & SfN, San Diego (USA) & Fast and stable discrimination in accentuated divergent-convergent synaptic connectivities \\
  2016  & CISS, Princeton (USA) & Non-parametric change point detection for spike trains \\
  2015  & UFABC (Brazil) &  Learning in insects: fan-in/fan-out structures  \\
  2015  & ICMC - USP (Brazil) &  On critical phenomena and power laws  \\
  2012  & IFSC - USP (Brazil) &  \LaTeX for thesis and dissertations  \\
\end{longtable}


\section{Other professional activities}

\begin{longtable}{p{2.5cm}p{14cm}}
  Reviewed for & PLOS Computational Biology, Neural Computation,
  Sensors and Actuator B, Royal Society Interface, Royal Society
  Philosophical Transactions A, NIPS, Elsevier's Heliyon.
\end{longtable}

\begin{longtable}{p{2.5cm}p{15cm}}
  2016 & Ad hoc reviewer for {\bf National Science Foundation} \\
  2015 & Participant of Brasil-USP iGEM team (gold badge)\\
  2013, 2015  & Judge during the {\bf IYPT} (finals in Brazil) \\
  2009 -- 2015 & Developed open LATEX thesis class for IFSC \\
  2012 & Developed JAQue (Joomla Academic Queries, closed source)
\end{longtable}


\section{Teaching experience}

\begin{longtable}{p{2.5cm}p{15cm}}
  2017 (Spring) & Invited lecture, EEB, UCLA \\
  2016 (Fall) & Lecturer for MGTF 415 Collecting \& Analyzing Financial Data, Rady School, UCSD \\
  2015 (Fall) & Invited lecture in Collecting \& Analyzing Financial Data -- Dr. Ramon Huerta, Rady School, UCSD \\
  2015 (Winter) & Helped teaching Collecting \& Analyzing Financial Data -- Dr. Ramon Huerta, Rady School, UCSD \\
  2010 -- 2013  & TA for Statistical Mechanics -- with Dr. Francisco Alcaraz, IFSC, USP \\
  2012  & TA for Physics 102 -- with Drs. PL Maia, JA Hoyos \& L Nunes, IFSC, USP \\
  2013  & TA for Computational Physics -- Dr. Francisco Alcaraz, IFSC, USP
\end{longtable}


\section{Outreach}

\begin{longtable}{p{1.8cm}p{15cm}}
  2016 & Advisor for a brazilian iGEM team (silver badge) \\
  2016 & Volunteer at Building With Biology Festival (Reuben Fleet Science Center, San Diego, CA USA) \\
  2015 & Conducted a large poll on Participation of Women in Brazilian Science, which was part of the 2015 iGEM project (gold badge). Results are publicly available \\
  2014 & Volunteer in Mozilla Software Carpentry bootcamp  (Dr. Andrea Zonca), hosted by the San Diego Super Computer Center, UCSD \\
  Since 2015 & Interaction with PyLadies Brazil, a group focused on balancing gender inequalities in Computer Science areas \\
  2012 & Contributed in the solutions to problems from IYPT for the brazilian team
\end{longtable}


\section{Publicly available datasets }

\begin{longtable}{p{1.0cm}p{15.5cm}}
  2016 & Recordings from two electric fish swimming freely. Published at FigShare. \\
  2016 & Gas sensors for home activity monitoring Data Set. Published at the UCI Machine Learning Repository \\
  2015 & pVeg promoter in E. Coli (iGEM 2015). Published in FigShare. \\
  2015 & GFP recordings from three different promoters from the Anderson Library (2015 Interlab Experiment). Published in FigShare.
\end{longtable}


\section{Other information}

{\bf Languages}

\begin{longtable}{p{3.5cm}p{10cm}}
  Native & Brazilian Portuguese \\
  Fluent & (American) English \\
  Intermediary & Italian, German and Japanese \\
\end{longtable}

{\bf Programming languages and Computer Skills}

\begin{longtable}{p{3.5cm}p{10cm}}
  {\bf Fluent} & C, C++, Fortran, Python, GAWK, and Unix bash shell \\
  High-level languages & Matlab, R, Maple \\
  Version control & Git, Mercurial, Fossial, GitHub \\
  Web oriented & PHP, HTML, Javascript, Jekyll, Bootstrap \\
  Databases & SQL, MySQL, Postgree, Apache Hadoop framework
\end{longtable}



\section{Abstracts in conferences}
\printbibliography[type=proceedings]


\end{document}
